Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-26 proposal/prop.tex
prop

\noindent It is easy to establish that quantum interval-valued
probability measures generalize conventional quantum probability
measures. In particular, any quantum probability measure can be recast
as an interval-valued measure using the three intervals
$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called
\unknown~because it provides no information. Given a quantum
probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
define a quantum interval-valued probability
measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where
$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
\[
\iota(x)=\begin{cases}
\necess & \textrm{if }x=1\textrm{ ;}\\
\imposs & \textrm{if }x=0\textrm{ ;}\\
\unknown & \textrm{otherwise.}
\end{cases}
\]
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question. Formally,
we can ask: what can we deduce about the state of a quantum system
given an interval-valued quantum probability measure, i.e., given
observations done with finite resources. In the case the intervals are
infinitely precise the question reduces to Gleason's theorem which
states that the state of the quantum system is uniquely determined by
the probability measure. But surely the less resources are availble,
the less precise the intervals, and the less we expect to know about
the state of the system. To formally state and answer this question we
begin with defining the \emph{core} and \emph{convexity} of a
probability measure as follows.

@@

\begin{example}[Three-dimensional quantum three-value interval-valued
  probability measure]\label{ex:three-dimensional-three-value} Given
  a three dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
    $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
  $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$, and
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})
  &=& \imposs\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})
  &=& \necess \\
\bar{\mu}(P) 
  &=& \unknown\quad\textrm{otherwise}
\end{eqnarray*}
It is straightforward to verify that $\bar{\mu}$ is a convex quantum
interval-valued probability measure. Now assume there exists a
real-valued quantum probability measure $\mu$ such that
$\mu(P)\in\bar{\mu}(P)$ for every event (projection)~$P$. We derive a
contradiction as follows. Suppose $\mu(P)\in\bar{\mu}(P)$ then we must
have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$. By Gleason's
theorem, there is a mixed
state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$ such that
$\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$, where
$\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$.  However, no pure
state~$\ket{\phi}$ can satisfy
$\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
\end{example}

\paragraph*{XXX.}

Recall that when approximating the probability classically, the quality
of the experimental equipment cannot be compensated by the number
of independent trials. If the precision of the intervals~$\mathscr{I}$
represents the quality of the quantum experimental equipment, example~\ref{ex:three-dimensional-three-value}
tells us that we cannot identify a particular state if the experimental
equipment reveals too little information. For example, $\bar{\mu}$
might correspond to $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
$\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$,
or the density matrix~$\frac{\mathbb{1}}{3}$ because $\bar{\mu}(\proj{\phi})\ne\necess$
for all $\ket{\phi}$. Also, example~\ref{ex:three-dimensional-three-value}
is no longer valid if our measurement equipment is a little more precise,
say $\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
because example~\ref{ex:three-dimensional-three-value} really use
the property of $\unknown$.

If we consider
$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
example~\ref{ex:three-dimensional-4-value} provides another example
with an empty core. Comparing to
example~\ref{ex:three-dimensional-three-value},
example~\ref{ex:three-dimensional-4-value} is closer to the Born rule
in a sense that it might only correspond to $\ket{2}$ or
$\frac{\mathbb{1}}{3}$, but not
$\ket{1}$. Example~\ref{ex:three-dimensional-4-value} is also no
longer valid for more precise measurement equipment as well.  In
general, we believe if the measurement equipment is more and more
precise, its interval-valued probability measure will be closer and
closer to the the Born rule. In the limit case,
$\mathscr{I}=\left\{ \left\{ a\right\}
  \middle|a\in\left[0,1\right]\right\} $
recovers conventional Gleason's theorem and the Born rule.

\begin{example}[Three-dimensional quantum 4-value interval-valued
probability measure]\label{ex:three-dimensional-4-value} 
Question: Is this convex? Given a three dimensional Hilbert space with
an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{
}$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
$\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$, and a quantum
$\mathscr{I}$-interval-valued probability
measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined as follow,
where the state vectors corresponding to 1-dimensional projector are
also illustrated in figure~\ref{fig:three-dimensional-4-value}.
\begin{enumerate}
\item Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \necess\textrm{ ,}
\end{eqnarray*}
 where $\ket{0}$ and $\ket{\ps}$ is illustrated as the red and green
dotted vector, respectively.
\item Consider the red and green circles in figure~\ref{fig:three-dimensional-4-value}.
They are the states orthogonal to $\ket{0}$ and $\ket{\ps}$, respectively,
and can be parametrized as $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
half of those states need special treatment, i.e., whenever $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we define 
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely\textrm{ .}
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely$. 
\end{enumerate}
That $\bar{\mu}$ has an empty core can be proved by contradiction.
Assume there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\[
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\]

Similar to example~\ref{ex:three-dimensional-three-value}, to verify
$\bar{\mu}$ is a quantum interval-valued probability measure, we
only need to verify equation~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
and it is sufficient to check 
\begin{equation}
\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{0}}\right)\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{2}}\right) & \subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{1}}\right)
\end{aligned}
\label{eq:non-additive-vectors}
\end{equation}
for every orthonormal basis~$\mathcal{B}=\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $.
We are going to enumerate all possible orthonormal bases to verify
equation~(\ref{eq:non-additive-vectors}), and case 1 and 2 are illustrated
in figure~\ref{fig:three-dimensional-4-value}. 
\begin{center}
\begin{figure}
\includegraphics[scale=0.4]{measure4.pdf}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates case
1 and 2 in $\mathbb{R}^{3}$ in example~\ref{ex:three-dimensional-4-value}.
The red and green dotted vector are $\ket{0}$ and $\ket{\ps}$ respectively.
All possible vectors of $\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\ps_{\theta,\gamma}^{\perp}}$
are drawn in the red and green circles, respectively. Within the circles,
a vector~$\ket{\psi}$ in dotted part means $\bar{\mu}(\proj{\psi})=\likely$;
otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is
a generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red
and green solid vectors are normalized $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$
and $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively.}
\end{figure}
\end{center}

\begin{enumerate}
\item When $\ket{\psi_{0}}$ is $\ket{0}$, then either $\ket{\psi_{1}}$
or $\ket{\psi_{2}}$ must be $\ket{0_{\theta,\gamma}^{\perp}}$ for
some $\theta$ and $\gamma$. Because of 
\[
\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
0\\
0
\end{pmatrix}\times\begin{pmatrix}0\\
\rme^{\rmi\gamma}\sin\theta\\
\cos\theta
\end{pmatrix}=\begin{pmatrix}0\\
-\cos\theta\\
\rme^{-\rmi\gamma}\sin\theta
\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}0\\
\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
\cos\left(\frac{\pi}{2}-\theta\right)
\end{pmatrix}=\rme^{-\rmi\gamma}\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}
\]
the pair $\ket{\psi_{1}}=\ket{0_{\theta,\gamma}^{\perp}}$ and $\ket{\psi_{2}}=\ket{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}$
for ($0<\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$) or $\theta=0$
enumerate all possible orthonormal bases. Equation~(\ref{eq:non-additive-vectors})
can then be verified as follow. 
\begin{equation}
\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0}\right)=\necess & \subseteq\likely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & =\unlikely\tensor*[_{\mathscr{I}}]{+}{}\imposs=\bar{\mu}\left(\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0}\right)\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\right)=\likely & =\imposs\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{0}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
\end{aligned}
\label{eq:case1}
\end{equation}
Similarly, when $\ket{\psi_{0}}$ is $\ket{\ps}$, equation~(\ref{eq:non-additive-vectors})
holds. 
\item When $\ket{0}\notin\mathcal{B}$ and $\ket{\psi_{0}}=\ket{0_{\theta,\gamma}^{\perp}}$
for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we want to
prove $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$.
Then, we have 
\begin{equation}
\begin{aligned}\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\unlikely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{1}}\right)=\likely & \subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\likely=\bar{\mu}\left(\proj{\psi_{2}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)
\end{aligned}
\label{eq:case2}
\end{equation}
In order to verify $\bar{\mu}\left(\proj{\psi_{1}}\right)=\bar{\mu}\left(\proj{\psi_{2}}\right)=\unlikely$,
it is sufficient to prove that if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
then ($0<\theta'<\frac{\pi}{2}$ and $\pi\le\gamma'<2\pi$) or $\theta'=\frac{\pi}{2}$.
Recall $\ip{\ps}{\ps_{\theta',\gamma'}^{\perp}}=0$. Hence, if $\ket{\ps_{\theta',\gamma'}^{\perp}}\in\mathcal{B}$,
we have $\ket{\ps_{\theta',\gamma'}^{\perp}}$ parallel to $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$.
\begin{equation}
\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}=\begin{pmatrix}1\\
1\\
0
\end{pmatrix}\times\begin{pmatrix}0\\
\rme^{\rmi\gamma}\sin\theta\\
\cos\theta
\end{pmatrix}=\begin{pmatrix}\cos\theta\\
-\cos\theta\\
\rme^{-\rmi\gamma}\sin\theta
\end{pmatrix}=\rme^{-\rmi\gamma}\begin{pmatrix}-\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
\rme^{\rmi\left(\pi+\gamma\right)}\sin\left(\frac{\pi}{2}-\theta\right)\\
\cos\left(\frac{\pi}{2}-\theta\right)
\end{pmatrix}=\sqrt{2}\rme^{-\rmi\gamma}\ket{\ps_{\frac{\pi}{2}-\theta,\pi+\gamma}^{\perp}}\label{eq:case2-cross}
\end{equation}
Because of $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we have
($0<\theta'=\frac{\pi}{2}-\theta<\frac{\pi}{2}$ and $\pi\le\gamma'=\pi+\gamma<2\pi$)
or $\theta'=\frac{\pi}{2}-\theta=\frac{\pi}{2}$. Similarly, when
$\ket{\psi_{0}}$ is $\ket{\ps_{\theta,\gamma}^{\perp}}$ and $\ket{\ps}\notin\mathcal{B}$,
equation~(\ref{eq:non-additive-vectors}) holds. 
\item Finally, when $\ket{0}\notin\mathcal{B}$, $\ket{\ps}\notin\mathcal{B}$,
$\ket{0_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$, and $\ket{\ps_{\theta,\gamma}^{\perp}}\notin\mathcal{B}$
for $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, i.e., the ``otherwise''
case. Then, equation~(\ref{eq:non-additive-vectors}) can easily
be verified. 
\begin{equation}
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi_{0}}\right)=\likely\subseteq\unlikely\tensor*[_{\mathscr{I}}]{+}{}\unlikely=\bar{\mu}\left(\proj{\psi_{1}}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(\proj{\psi_{2}}\right)\label{eq:case3}
\end{equation}
\end{enumerate}
\end{example}

The following example verifies example~\ref{ex:three-dimensional-4-value}
cannot hold with more precise intervals.

\begin{example}[Three-dimensional quantum 4-value interval-valued
probability measure (Continue)]\label{ex:three-dimensional-4-value-1}
Consider $\mathscr{I}=\left\{ \imposs,\left[l_{1},r_{1}\right],\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right],\necess\right\} $,
where $\left[l_{1},r_{1}\right]$ and $\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]$
will be used to replace every $\unlikely$ and $\likely$ in example~\ref{ex:three-dimensional-4-value},
respectively. The bound of $l_{1}$ and $r_{1}$ can then be estimated
by the equations corresponding to equation~(\ref{eq:case1}), (\ref{eq:case2}),
and (\ref{eq:case3}).

When we replace $\unlikely$ and $\likely$ by $\left[l_{1},r_{1}\right]$
and $\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]$,
equation~(\ref{eq:case1}) will become

\begin{equation}
\begin{aligned}\necess & \subseteq\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
\left[l_{1},r_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\imposs\\
\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right] & \subseteq\imposs\tensor*[_{\mathscr{I}}]{+}{}\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]
\end{aligned}
\label{eq:case1-1}
\end{equation}
which are all tautologies. Equation~(\ref{eq:case2}) will become
\begin{equation}
\begin{aligned}\left[l_{1},r_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\\
\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right] & \subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]
\end{aligned}
\label{eq:case2-1}
\end{equation}
which implies $l_{1}=0$. Finally, equation~(\ref{eq:case3}) will
become
\begin{equation}
\left[1\tensor*[_{\mathbb{R}}]{-}{}r_{1},1\tensor*[_{\mathbb{R}}]{-}{}l_{1}\right]\subseteq\left[l_{1},r_{1}\right]\tensor*[_{\mathscr{I}}]{+}{}\left[l_{1},r_{1}\right]\label{eq:case3-1}
\end{equation}
which implies $\frac{1}{2}\le r_{1}\le1$. Therefore, $l_{1}=0$ and
$r_{1}=\frac{1}{2}$ provides the most precise intervals which make
example~\ref{ex:three-dimensional-4-value} work, and in this case,
the intervals are $\left\{ \imposs,\unlikely,\likely,\necess\right\}
$.
\end{example}

Although it is easier to deduce an interval-valued probability measure
has an empty core by considering the state mapped to $\imposs$ as
in example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
it is not the only way to prove an interval-valued probability measure
has an empty core. The following family of interval-valued probability
measures satisfy that $\bar{\mu}\left(P\right)=\imposs$ if and only
if $P=\mathbb{0}$, but we can still prove them have empty cores.

Although it is easier to deduce an interval-valued probability measure
has an empty core by considering the state mapped to $\imposs$ as
in example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
it is not the only way to prove an interval-valued probability measure
has an empty core. The following family of interval-valued probability
measures satisfy that $\bar{\mu}\left(P\right)=\imposs$ if and only
if $P=\mathbb{0}$, but we can still prove them have empty cores.

\paragraph*{Research Question.} confirm that we get closer and closer
to Born rule as precision improves; find conditions on interval-valued
quantum prob. measures that would make sense; precision improves
implies states get sharper

>>>>

\noindent It is easy to establish that quantum interval-valued
probability measures generalize conventional quantum probability
measures. In particular, any quantum probability measure can be recast
as an interval-valued measure using the three intervals
$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called
\unknown~because it provides no information. Given a quantum
probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
define a quantum interval-valued probability
measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where
$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
\[
\iota(x)=\begin{cases}
\necess & \textrm{if }x=1\textrm{ ;}\\
\imposs & \textrm{if }x=0\textrm{ ;}\\
\unknown & \textrm{otherwise.}
\end{cases}
\]
This measure represents the beliefs of an experimenter with no prior 
knowledge about the particular quantum system in question. Formally,
we can ask: what can we deduce about the state of a quantum system
given an interval-valued quantum probability measure, i.e., given
observations done with finite resources. In the case the intervals are
infinitely precise the question reduces to Gleason's theorem which
states that the state of the quantum system is uniquely determined by
the probability measure. But surely the less resources are available,
the less precise the intervals, and the less we expect to know about
the state of the system. To formally state and answer this question we
begin with defining the \emph{core} and \emph{convexity} of a
probability measure as follows.

@@

\begin{example}[Three-dimensional three-interval-valued quantum
  probability measure]\label{ex:three-dimensional-three-value} Given
  a three dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
    $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
  $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$, and
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})
  &=& \imposs\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})
  &=& \necess \\
\bar{\mu}(P) 
  &=& \unknown\quad\textrm{otherwise}
\end{eqnarray*}
It is straightforward to verify that $\bar{\mu}$ is a convex quantum
interval-valued probability measure. Now assume there exists a
real-valued quantum probability measure $\mu$ such that
$\mu(P)\in\bar{\mu}(P)$ for every event (projection)~$P$. We derive a
contradiction as follows. Suppose $\mu(P)\in\bar{\mu}(P)$ then we must
have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$. By Gleason's
theorem, there is a mixed
state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$ such that
$\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$, where
$\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$.  However, no pure
state~$\ket{\phi}$ can satisfy
$\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
\end{example}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{measure4.pdf}
\end{center}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates
  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
  and $\ket{\ps}$ respectively.  All possible vectors of the subspaces
  $\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
  circles, respectively. Within the circles, a dotted
  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
  green solid vectors are normalized
  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively.}
\end{figure}

Looking closely at the example above, we might think that the
probability measure $\bar{\mu}$ is induced by the state $\ket{2}$
because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, or we
might think it is induced by the state $\ket{1}$ because
$\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, or yet we might
think it is induced by the mixed state $\frac{\mathbb{1}}{3}$ because
$\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$. Each of these
possibilities is compatible with some but not all of the
observations. All is not lost however: if the observations are made
more precise, we conjecture that some of the inconsistencies
disappear. A partial proof of this conjecture is the following example
which refines the previous probability measure by adding more precise
intervals. It remains to prove that this refined measure is convex,
however.

\begin{example}[Three-dimensional four-interval-valued quantum
  probability measure]\label{ex:three-dimensional-4-value}
  Given a three dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
  }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and
  $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$. The definition of
  $\bar{\mu}$ below refers to Fig.~\ref{fig:three-dimensional-4-value}
  which plots the 1-dimensional projectors:
\begin{enumerate}
\item Let:
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) 
  &=& \imposs \\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) 
  &=& \necess
\end{eqnarray*}
where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green dotted
vectors, respectively.
\item The red and green circles are are the states orthogonal to
  $\ket{0}$ and $\ket{\ps}$, respectively, and can be parametrized as
  $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
  and
  $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
  where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
  half of those states need special treatment, i.e., whenever
  $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)
  &=& \likely \\
\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right)=
  \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right) 
  &=& \unlikely
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
\end{enumerate}
It is straightforward but tedious to check that $\bar{\mu}$ is an
interval-valued quantum probability measure. Although we have not
verified that $\bar{\mu}$ is convex, the following argument
establishes that is has an empty core. Assume there is a real-valued
probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for
all $P\in\events$. Because
$\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$ and
$\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$, we must
have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$ so that
$\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However,
\[
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\]
This measure however is ``better'' than the previous one in the sense
that it might only be induced by $\ket{2}$ or the density matrix
$\frac{\mathbb{1}}{3}$, but not by
$\ket{1}$. 
\end{example}

In general, we conjecture that if the measurement equipment is made
more and more precise, the corresponding interval-valued probability
measure will be closer and closer to the Born rule. In the limit case,
$\mathscr{I}=\left\{ \left\{ a\right\}
  \middle|a\in\left[0,1\right]\right\}$
we do indeed recover the conventional Gleason's theorem and the Born
rule.

\paragraph*{Research Question.} Confirm that as the number and
precision of the intervals increase the interval-valued quantum
probability measure converges to the measure induced by the Born
rule.
